POODLE 1.0 - To the core of your data

### 2016-01-12 poodle_project/paper/main.tex
paper auf dem neuesten stand und format ein bisschen angepasst

\enlargethispage{12pt}

\subsection{A real world pipeline}
function study
\subsection{cloning as lab strategy}
Toolkit idea
\subsection{cloning methods}
Classsic Cloning, Quickchange, Restriction free cloning

@@

Our software package provides not just a database functionality for powerful and safe data storage 
and an easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This function 
is implemented by using a combination of Blast binaries provided by NCBI and the Biojava Api 
(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
The remote Blast search is not a fully functional copy of the NCBI web service but can be used to 
perform a quick and simple search against databases provided by NCBI, e.g. Swissprot (\citealp{Doni01}). But we 
do not recommend to overuse that because too many requests may cause a blacklisting by NCBI. This 
remote Blast routine is mainly for the insertion of a new entry. The idea is to check whether there 
are information about the new sequence. But it can also used separated from the new entry routine. 
The local Blast routine does everything someone would 
expect from a Blast search but against the local database, hence local Blast. There a several programs, 
e.g. blastn or blastp, available for both Blast methods.

@@

\bibitem[O'Donavan {\it et~al}., 2002]{Doni01}
O'Donovan, C., Martin, M.J., Gattiker, A., Gasteiger, E., Bairoch, A., Apweiler, R. (2002) High-quality protein knowledge resource: SWISS-PROT and TrEMBL {\it Brief. Bioinform.}  {\bf 3} (3), 275-284. doi: 10.1093/bib/3.3.275

>>>>

\enlargethispage{12pt}
The POODLE project is a project which deals with really daily duty in a bio laboratory. Due to the data managment aspect of sequences and the task providing information fast, the project is clearly settled in the computer science field. The background data, which was obtained, was focussed on cloning for protein function studies or structure elucidation. Therefore we will focus on this application of the POODLE.

\subsection{A real world pipeline}
The cloning procedure is a standard strategy, which is used in nearly every life science lab. One possible application is in protein structure-function relationship studies. These studies use proteins, with a known sequence and start to modify the sequence with mutationsin order to observe changes  in the protein structure or functional bahaviour. The general pipeline of such an experiment could be, introducing the mutation via cloning, isolating the mutated protein and visualisation of differences via several methods. The visualisation for example could be an NMR interaction study or via X-Ray-Crystallography or any other essay. POODLE trys to manage the first  step of this pipeline, which is not only in this pieline the basic step.
\subsection{cloning as lab strategy}
Cloning is the key to a huge ammount of variety in the resulting protein constructs. Via cloning, it is possible to remove a function, add a function to a protein or influence the structure. Today, there are many different cloning methods available, like the classical restriction approach, the site directed mutagenisis method, restriction free cloning or the Crisp-Cas system. All mehtods have a specific task and are chosen in various situation. For this paper we want to stick to the site directed mutagenisis, which was initially developed by stratagene as QuickChange site-directed mutagensis kit. This method allow to introduce small directed mutation into a protein on DNA level. these mutations can be used to perform point mutations or switch single or multiple amino acids.

\begin{figure}
	\includegraphics[width=0.4\textwidth]{"../Documents/img/QC-cloning.png}
	\caption{Schema of QC}
	\label{QC-pic}
\end{figure}

\subsection{cloning methods}
Classsic Cloning, Quickchange, Restriction free cloning

@@

Our software package provides not just a database functionality for powerful and safe data storage 
and an easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This function 
is implemented by using a combination of Blast binaries provided by NCBI and the Biojava Api 
(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
The remote Blast search is not a fully functional copy of the NCBI web service but can be used to 
perform a quick and simple search against databases provided by NCBI, e.g. Swissprot (\citealp{Donavan01}). But we 
do not recommend to overuse that because too many requests may cause a blacklisting by NCBI. This 
remote Blast routine is mainly for the insertion of a new entry. The idea is to check whether there 
are information about the new sequence. But it can also used separated from the new entry routine. 
The local Blast routine does everything someone would 
expect from a Blast search but against the local database, hence local Blast. There a several programs, 
e.g. blastn or blastp, available for both Blast methods.

@@

\bibitem[O'Donavan {\it et~al}., 2002]{Donavan01}
O'Donovan, C., Martin, M.J., Gattiker, A., Gasteiger, E., Bairoch, A., Apweiler, R. (2002) High-quality protein knowledge resource: SWISS-PROT and TrEMBL {\it Brief. Bioinform.}  {\bf 3} (3), 275-284. doi: 10.1093/bib/3.3.275

\bibitem[Alberts {\it et~al}., 2002]{Alberts01}
Alberts B, Johnson A, Lewis J, et al. (2002) Molecular Biology of the Cell. 4th edition. {\it New York: Garland Science}. Studying Gene Expression and Function. Available from: http://www.ncbi.nlm.nih.gov/books/NBK26818/
